---
title: "SWC R Markdown Test"
author: "Karl Broman"
date: "April 28, 2015"
output: html_document
---

```{r, global_knitr_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, 
                      fig.path="../Figs/firsttry_",
                      fig.height=8, fig.width=11)
```

This is a test document to show you how to use R Markdown.

The sun did not shine,  
it was to wet to play,  
so we sat in the house  
all that cold, cold wet day.  

```{r, load_library, include=FALSE}
# I'll need these later
library(dplyr)
library(ggplot2)
```

```{r, load_data}
gapminder <- read.csv("../data/gapminder.csv")
```

Here are the first five lines of the data.

```{r, head_gapminder}
head(gapminder)
```

This gapminder data has `r nrow(gapminder)` rows and `r ncol(gapminder)` columns.

```{r ave_life_exp_for_china, include=FALSE}
ale_china <- gapminder %>%
  filter(country=="China") %>%
  summarize(ave=mean(lifeExp))
another_number <- 23.0353
```

I get the average life expectancy, averaged across these years (if it means anything) for China is `r round(ale_china, 1)`.

```{r broman_pkg}
library(broman)
```

Another number is `r myround(another_number, 1)`.

```{r hist_life_exp, fig.height=4}
ggplot(gapminder, aes(x=lifeExp)) + 
  geom_histogram()
```

This next one should be taller:

```{r hist_life_exp_tall}
ggplot(gapminder, aes(x=lifeExp)) + 
  geom_histogram()
```









